Tropical Andes plant trait data TRY

### 2025-08-27 code/L0/L0_TropicalAndes_plants_TRY.Rmd
Still cannot import TRY data

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php on 2023-10-24
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/29548_24102023041242/29548.txt")
```

>>>>

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php on 2023-10-24
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY_2023/29548_24102023041242/29548.txt")
```
